---
title: "RWorksheet_guion#1.Rmd"
author: "Mikyla Grace Guion"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31,
27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 
17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```
# a. How many data points?
```{r}
length(age)
```
# b. Write the code and its output.
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31,
27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 
17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```

2.
```{r}
reciprocal <- 1/age
library("MASS")
fractions(reciprocal)
```

3.
```{r}
new_age <- c(age, 0, age)
print(new_age)
```

# When new_age is printed, the same values of age is printed, then 0, then the values of age again.

4.
```{r}
sort(age)
```

5.
```{r}
min(age)
max(age)
```

6.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
```
# a.How many data points?
```{r}
length(data)
```
# b.Write the R code and its output.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
```

7. 
```{r}
data2 <- data
data * 2
```
# The data doubled its value.

8.
8.1
```{r}
seq(1:100)
```
8.2
```{r}
seq(20,60)
```
8.3
```{r}
mean(20:60)
```
8.4
```{r}
sum(51:91)
```
# a.How many data points from 8.1 to 8.4?
```{r}
length(seq) + length(seq) + length(mean) + length(sum)
```
# b. Write the R code and its output from 8.1 to 8.4.
8.1
```{r}
seq(1:100)
```
8.2
```{r}
seq(20,60)
```
8.3
```{r}
mean(20:60)
```
8.4
```{r}
sum(51:91)
```
```{r}
length(integer)+length(mean)+length(sum)
```
# c.For 8.5 find only maximum data points until 10. 
8.5 *
```{r}
thousands <- seq(1:1000)
thousands
```
```{r}
max(thousands[thousands <-10])
```

9.
```{r}
Filter(function(i) { all(i %% c(3,5,7) !=0)}, seq(100))
```

10.
```{r}
backwards <- seq(100, 1)
print(backwards)
```

11. *
```{r}
numbers <- 1: 24
multiples <- numbers[numbers %% 3 == 0 | numbers %% 5 == 0]
print(multiples)
sum_multiples <- sum(multiples)
print(sum_multiples)
```

12. 
```{r}
#x <- {0 + x + 5 + }
```
# Describe the output

- The output shows error because of the trailing plus sign. 

13. 
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
score [2]
score [3]
```

14.
```{r}
a = c(1,2,NA,4,NA,6,7)
print(a, na.print="-999")
```
# Describe the output
- When I run the vector first, it printed out the values exactly including the NA. However, when I run the it again after entering the print function, the NA changed into -999.

15.
```{r}
name <- readline(prompt="Input your name: ")
age <- readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```
# Describe the output
- The program prompts the user to enter their name and age. Afterwards, the inputs are stored into the name object and age object respectively. The inputs are then showed in the printed statement because the object is called.
