---
title: "RWorksheet_guion#2"
author: "Mikyla Grace Guion"
date: "2024-09-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.
a.
```{r}
vec <- -5:5
print(vec)
```
# The vector prints out values from -5 to 5 consecutively
b.
```{r}
x <- 1:7
print(x) 
```
2.
a.
```{r}
vec2 <- seq(1,3, by=0.2)
print(vec2)
```
# The output shows values from 1 to 3, incremented by 0.2
3.
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
          24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
          18)
```
a.
```{r}
third <- ages[3]
print(third)
```
b.
```{r}
secondAndFourth <- ages[c(2,4)]
print(secondAndFourth)
```
c.
```{r}
but <- ages[-c(4,12)]
print(but)

```
4.
b.
```{r}
x <-c("first"=3, "second"=0, "third"=9)
```
a.
```{r}
names(x)
x[c("first", "third")]
```
# The output prints out a table which shows the strings: first and third on the first row and aligned with its corresponding values: 3 and 9 on the second row. 
5.
b.
```{r}
x <- -3:2
```
a.
```{r}
x[2] <- 0
print(x)
```
#The output shows a vector from -3 to 2 consecutively. However, after I modified the second element, it changed into 0 (previously -2).  
6.
a.
```{r}
cruz <- data.frame(
  Month = c("Price per liter(PhP)", "Purchase-quantity(Liters)"),
  Jan = c(format(52.50, nsmall = 2), 25),                   
  Feb = c(format(57.25, nsmall = 2), 30),
  March = c(format(60.00, nsmall = 2), 40),
  Apr = c(format(65.00, nsmall = 2), 50),
  May = c(format(74.25, nsmall = 2), 10),
  June = c(format(54.00, nsmall = 2), 45)
)
print(cruz)
```

b.

```{r}
liter <- as.numeric(cruz[1, -1])  
purchase <- as.numeric(cruz[2, -1])
wm <- weighted.mean(liter, purchase)
print(wm) 
```
7.
c.
a.
```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
          sd(rivers), min(rivers), max(rivers))
```
b.
```{r}
print(data)
```
8.
a.
```{r}
PowerRanking <-c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)

CelebName <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson", "Dr. Phil McGaw", "Jay Lenon", "Celine Dion", "Kobe Bryant")

Pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31 )

print(PowerRanking)
print(CelebName)
print(Pay)
```
b.
```{r}
JK<- which(CelebName == "J.K Rowling")

PowerRanking <- PowerRanking [-JK]
CelebName <- CelebName[-JK]
Pay <- Pay[-JK]

PowerRanking <- append(PowerRanking, 15, after = 14)
CelebName <- append(CelebName, "J.K Rowling", after = 14)
Pay <- append(Pay, 90, after = 14)

print(PowerRanking)
print(CelebName)
print(Pay)
```
c.

```{r}
data <- read.csv("PowerRanking.csv")
print(data)
```
d.
```{r}
SubsetData <- data[10:20, ]
save(SubsetData, file = "Ranks.RData")
print(SubsetData)
```
e.
#The output shows only rows from 10 until 20

9.
a.
```{r}
data <- read_excel("hotels-vienna.xlsx")
print(data)
```





10.
a.
```{r}
vegetables <- c("Carrot", "Potato", "Spinach", "Corn", "Cucumber", "Okra", "Cabbage", "Cauliflower", "Tomato", "Pumpkin")
print(vegetables)
```
b.
```{r}
vegetables <- c(vegetables, "Lettuce","Onion")
print(vegetables)
```
c.
```{r}
vegetables <- append(vegetables, c("Bitter Gourd", "Garlic", "Beetroot", "Eggplant"), after = 5)
print(vegetables)
length(vegetables)
```
d.
```{r}
vegetables <- vegetables[-c(5, 10, 15)]
print(vegetables)
length(vegetables)
```






