---
title: "RWorksheet_guion#4a"
author: "Mikyla Grace Guion"
date: "2024-10-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Create a data frame.
```{r}
houseHo <- data.frame(
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5,13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0,  13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0,                 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)
houseHo
```

# a. Describe the data
The data Household Data shows the shoe size, height, and gender.

# b. Create a subset by males and females with their corresponding shoe size and height.
```{r}
male_data <- subset(houseHo, Gender == "M", select = c(Shoe_size, Height))
female_data <- subset(houseHo, Gender == "F", select = c(Shoe_size, Height))
male_data
female_data
```

# c. Find the mean of shoe size and height of the respondents.
```{r}
mean(houseHo$Shoe_size)
mean(houseHo$Height)
```

# d. Is there a relationship between shoe size and height? Why?
Yes, the greater the the height the bigger shoe size it ranges. However, if you look at it closely it's not consistent. For instance, one female has a height of 59.0 and the other 62.0 and their shoe sizes are 8.5 and 5.0 respectively.

# 2.Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months_vector <- c("March", "April", "January", "November", "January",
                   "September", "October", "September", "November", "August",
                   "January", "November", "November", "February", "May", "August",
                   "July", "December", "August", "August", "September", 
                   "November", "February", "April")
factor_months_vector <- factor(months_vector)
factor_months_vector
```

# 3.Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?
```{r}
summary(months_vector)
summary(factor_months_vector)
```
The summary of months_vector only shows how many values the vector contains and the data type while the summary of factor_months_vector shows the frequency of each month or level. The summary of the factor is more useful since it provides clearer details about the values. 

# 4. Create a vector and factor
```{r}
factor_data <- c("East", "West", "North")
frequency_vector <- c(1, 4, 3)

new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```
# 5.
# a. Import the excel file into the Environment Pane using read.table() function.  
```{r}
data <- read.table("import_march.csv", header = TRUE, sep = ",")
```

# b. View the dataset. Write the R scripts and its result.

```{r}
data
```

