---
title: "RWorksheet_guion#4b"
author: "Mikyla Grace Guion"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Using the for loop, create an R script that will display a 5x5 matrix as shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.
```{r}
vectorA = c(1,2,3,4,5)
matri <- matrix(0, nrow = 5, ncol = 5)
  for(i in 1:5) {
    for(j in 1:5) {
      matri[i,j] <- abs(vectorA[i] - vectorA[j])
    }
    print(matri[i,j])
  }
```
# 2. Print the string "*" using for() function. The output should be the same as shown in Figure
```{r}
for(i in 1:5) {
  line <- rep('"*"', i)
  cat(line, sep= " ")
  cat("\n")
}
```
# 3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.

# 4.

# a. What is the R script for importing an excel or a csv file? Display the first 6 rows of the dataset? Show your codes and its result

# b. Create a subset for gender(female and male). How many observations are there in Male? How about in Female? Write the R scripts and its output.

# c. Create a graph for the number of males and females for Household Data. Use plot(), chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and its result.

# 5.

# a. Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.

# 6.

# a. Check for the structure of the dataset using the str() function. Describe what you have seen in the output.

# b. Create an R object that will contain the mean of the sepal.length, sepal.width,petal.length,and petal.width. What is the R script and its result?

# c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write the R script and its result.

# d. Subset the species into setosa, versicolor, and virginica. Write the R scripts and show the last six (6) rows of each species.

# e. Create a scatterplot of the sepal.length and sepal.width using the different species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal width and length, labels for the x and y axis, the pch symbol and colors should be based on the species.

# f. Interpret the result.

# 7.

# a. Rename the white and black variants by using gsub() function.

# b. b. Get the total number of each variations and save it into another object. Save the object as variations.RData. Write the R scripts. What is its result?

# c. From the variations.RData, create a barplot(). Complete the details of the chart which include the title, color, labels of each bar.

# d. Create a barplot() for the black and white variations. Plot it in 1 frame, side by side. Complete the details of the chart.
