---
title: "RWorksheet_guion#4b"
author: "Mikyla Grace Guion"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Using the for loop, create an R script that will display a 5x5 matrix as shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.
```{r}
vectorA = c(1,2,3,4,5)
matri <- matrix(0, nrow = 5, ncol = 5)
  for(i in 1:5) {
    for(j in 1:5) {
      matri[i,j] <- abs(vectorA[i] - vectorA[j])
    }
    print(matri[i,j])
  }
```
# 2. Print the string "*" using for() function. The output should be the same as shown in Figure
```{r}
for(i in 1:5) {
  line <- rep('"*"', i)
  cat(line, sep= " ")
  cat("\n")
}
```
# 3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.
```{r}
Fibonacci <- function(start){
  n <- 0
  n1 <- 1
  n2 <- 0
  
  if (start == 1){
      cat(n, "", n1, "", n1, " ")
  }
  
  for (i in 0:start){
    n2 <- n + n1
    n <- n1
    n1 <- n2
  }
  
  repeat{
    if (n2 > 500) break
    cat(n2, " ")
    n2 <- n + n1
    n <- n1
    n1 <- n2
  }
}

start <- readline(prompt = "Enter starting term: ")
Fibonacci(start)

```


# 4.

# a. What is the R script for importing an excel or a csv file? Display the first 6 rows of the dataset? Show your codes and its result
```{r}
shoe <- read_excel("shoe_size.xlsx")
head(shoe)
```

# b. Create a subset for gender(female and male). How many observations are there in Male? How about in Female? Write the R scripts and its output.
```{r}
female_subset <- subset(shoe, Gender == "F")
male_subset <- subset(shoe, Gender == "M")

female_count <- nrow(female_subset)
male_count <- nrow(male_subset)

female_count
male_count
```
# c. Create a graph for the number of males and females for Household Data. Use plot(), chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and its result.
```{r}
gender_counts <- table(shoe$Gender)
barplot(gender_counts,
        main = "Number of Males and Females",
        xlab = "Gender",
        ylab = "Count",
        col = c("lightblue", "pink"),
        legend = c("Male", "Female"),
        names.arg = c("Male", "Female"))
```
# 5.

# a. Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.
```{r}
categories <- c("Food", "Electricity", "Savings", "Miscellaneous")
expenses <- c(60, 10, 5, 25)

percentages <- round((expenses / sum(expenses)) * 100)
labels <- paste(categories, percentages, "%")

pie(expenses,
    labels = labels,
    col = c("violet", "orange", "green", "red"),
    main = "Household Expenses Distribution")

```
# 6.

# a. Check for the structure of the dataset using the str() function. Describe what you have seen in the output.
```{r}
data(iris)
str(iris)
```
# b. Create an R object that will contain the mean of the sepal.length, sepal.width,petal.length,and petal.width. What is the R script and its result?
```{r}
MeanSeL <- mean(iris$Sepal.Length)
MeanSeW <- mean(iris$Sepal.Width)
MeanPeL <- mean(iris$Petal.Length)
MeanPeW <- mean(iris$Petal.Width)

MeanSeL 
MeanSeW 
MeanPeL
MeanPeW
```
# c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write the R script and its result.
```{r}
species_counts <- table(iris$Species)

pie(species_counts,
    main = "Iris Species Distribution",
    legend = names(species_counts),
    col = c("violet", "lightblue", "pink"))
  

```
# d. Subset the species into setosa, versicolor, and virginica. Write the R scripts and show the last six (6) rows of each species.
```{r}
Setosa <- subset(iris, Species == "setosa")
Versicolor <- subset(iris, Species == "versicolor")
Virginica <- subset(iris, Species == "virginica")

tail(Setosa)
tail(Versicolor)
tail(Virginica)
```
# e. Create a scatterplot of the sepal.length and sepal.width using the different species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal width and length, labels for the x and y axis, the pch symbol and colors should be based on the species.
```{r}
colors <- c("setosa" = "violet", "versicolor" = "lightblue", "virginica" = "pink")
pch_symbols <- c("setosa" = 16, "versicolor" = 17, "virginica" = 18)

plot(iris$Sepal.Length, iris$Sepal.Width,
     col = colors[iris$Species],
     pch = pch_symbols[iris$Species],
     main = "Iris Dataset",
     sub = "Sepal Width and Length",
     xlab = "Sepal Length",
     ylab = "Sepal Width")

legend("topright", legend = levels(iris$Species), 
       col = c("violet", "lightblue", "pink"),
       pch = c(16, 17, 18),
       title = "Species")
```
# f. Interpret the result.
The scatter plot shows the sepal width of each specie on the y axis and sepal length on the x axis. It also shows different shapes and color to represent each specie. When looking at the scatter plot, there is a significant difference between the sizes of the setosa from the versicolor and virginica. Versicolor and virginica species overlap with each other which means they are quite similar with their size.

# 7.

# a. Rename the white and black variants by using gsub() function.

# b. b. Get the total number of each variations and save it into another object. Save the object as variations.RData. Write the R scripts. What is its result?

# c. From the variations.RData, create a barplot(). Complete the details of the chart which include the title, color, labels of each bar.

# d. Create a barplot() for the black and white variations. Plot it in 1 frame, side by side. Complete the details of the chart.
